---
title: "Simulation Results"
format: html
editor: visual
---

## Simulation Design

-   Outcome-specific ICC: 0.01, 0.025, 0.05

-   Intersubject between-outcomes ICC: 0.005, 0.025

-   Intrasubject between-outcomes ICC: 0.2, 0.5

-   Bayes factor threshold: 5 and 10

-   Probability: 0.8

## Intersection-Union Test

### Test-specific Factors

Treatment effects: 0.3, 0.5, 0.7, 0.9

Avoiding the same treatment effects for both outcomes and repeating the combination.

### Plots

```{r data}
# Libraries
library(ggplot2)
library(rlang)
library(dplyr)

source("~/GitHub/SSD-Multivariate-CRT/scripts/functions_plots.R")

final_results_findN2 <- readRDS("~/GitHub/SSD-Multivariate-CRT/scripts/FindN2_iu_new/final_results_findN2.RDS")
head(final_results_findN2)
```

#### Main Effects

##### Outcome Specific ICC

```{r}
main_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "out_specific_ICC", fixed = c("eff_size1", "eff_size2", "intersubj_between_outICC", "intrasubj_between_outICC", "BF_thresh"), val_fixed = c(0.3, 0.5, 0.005, 0.2, 10), color_labs = "Outcome specific \nICC", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right")
```

##### Intersubject Between-Outcomes ICC

```{r}
main_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "intersubj_between_outICC", fixed = c("eff_size1", "eff_size2", "out_specific_ICC", "intrasubj_between_outICC", "BF_thresh"), val_fixed = c(0.3, 0.5, 0.025, 0.2, 10), color_labs = "Intersubject between \noutcomes ICC", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right")
```

##### Intrasubject Between-Outcomes ICC

```{r}
main_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "intrasubj_between_outICC", fixed = c("eff_size1", "eff_size2", "out_specific_ICC", "intersubj_between_outICC", "BF_thresh"), val_fixed = c(0.3, 0.5, 0.025, 0.025, 10), color_labs = "Intrasubject between \noutcomes ICC", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right")
```

##### Effect Sizes

```{r}
results_findN2_effe_sizes <- cbind(final_results_findN2, effect_sizes =factor(paste(final_results_findN2$eff_size1, final_results_findN2$eff_size2)))
main_eff_plot(results_findN2_effe_sizes, x = "n1.final", y = "n2.final", grouping = "effect_sizes", fixed = c("out_specific_ICC", "intersubj_between_outICC", "intrasubj_between_outICC", "BF_thresh"), val_fixed = c(0.025, 0.025, 0.5, 10), color_labs = "Effect sizes \n(Eff1, Eff2)", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right")
```

##### Bayes Factor Threshold

```{r}
main_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "BF_thresh", fixed = c("eff_size1", "eff_size2", "out_specific_ICC", "intrasubj_between_outICC", "intersubj_between_outICC"), val_fixed = c(0.3, 0.5, 0.05, 0.5, 0.025), color_labs = "Bayes factor \nthreshold", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right")
```

#### Interactions

##### ICCs

```{r}
inter_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "intersubj_between_outICC", fixed = c("eff_size1", "eff_size2", "BF_thresh"),val_fixed = c(0.3, 0.5, 10), color_labs = "Intersubject between \noutcomes ICC", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right", panels = c("out_specific_ICC", "intrasubj_between_outICC"))
```

Columns: Intrasubject between-outcomes ICC

Rows: Outcome specific ICC

##### ICC and Threshold

```{r}
inter_eff_plot(final_results_findN2, x = "n1.final", y = "n2.final", grouping = "BF_thresh", fixed = c("eff_size1", "eff_size2", "intersubj_between_outICC"),val_fixed = c(0.3, 0.5, 0.005), color_labs = "Bayes factor \nthreshold", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right", panels = c("out_specific_ICC", "intrasubj_between_outICC"))
```

Columns: Intrasubject between-outcomes ICC

Rows: Outcome specific ICC

##### ICC and Effect Sizes

```{r}
inter_eff_plot(results_findN2_effe_sizes, x = "n1.final", y = "n2.final", grouping = "effect_sizes", fixed = c("intersubj_between_outICC", "BF_thresh"),val_fixed = c(0.005, 10), color_labs = "Effect sizes \n(Eff1, Eff2)", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right", panels = c("out_specific_ICC", "intrasubj_between_outICC"))
```

Columns: Intrasubject between-outcomes ICC

Rows: Outcome specific ICC

##### Threshold, effect sizes and outcome-specific ICC

```{r}
inter_eff_plot(results_findN2_effe_sizes, x = "n1.final", y = "n2.final", grouping = "effect_sizes", fixed = c("intersubj_between_outICC", "intrasubj_between_outICC"),val_fixed = c(0.025, 0.5), color_labs = "Effect sizes \n(Eff1, Eff2)", xlab = "Cluster size", ylab = "Number of clusters", legend_pos = "right", panels = c("out_specific_ICC", "BF_thresh"))
```

Columns: Bayes factor threshold

Rows: Outcome specific ICC
